---
title: "reach.viz: flood visualisation for the Flode ecosystem"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{reach.viz overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  fig.width  = 7,
  fig.height = 4,
  dpi = 120
)
library(reach.viz)
library(data.table)
```

`reach.viz` provides the team's standard ggplot2 theme and a catalogue of
flood-specific plot functions. Every function accepts a `data.table` input and
returns a `ggplot` object that can be composed with further layers.

---

## Theme

```{r theme-example}
library(ggplot2)
ggplot(data.frame(x = 1:10, y = cumsum(rnorm(10))), aes(x, y)) +
  geom_line(colour = "#009FAF", linewidth = 0.8) +
  labs(title = "theme_flood() example", x = "Time step", y = "Value") +
  theme_flood()
```

---

## Hydrometric time series

```{r hydrograph-example}
dt <- make_hydro_dt()
plot_hydrograph(dt[site_id == "SITE_A"], title = "Hourly flow: Site A")
```

```{r hydrograph-facet}
plot_hydrograph(dt, site_col = "site_id", title = "Both sites")
```

---

## QC overview

```{r qc-heatmap}
plot_qc_heatmap(dt, period = "month")
```

```{r data-availability}
plot_data_availability(dt)
```

---

## Ensemble forecasts

```{r ensemble-ribbon}
ens <- make_ensemble_dt()
plot_ensemble_ribbon(ens)
```

```{r ensemble-spaghetti}
plot_ensemble_spaghetti(ens, alpha = 0.2)
```

```{r exceedance}
plot_exceedance_probability(ens, thresholds = c(Alert = 50, Warning = 90, Severe = 130))
```

---

## Model performance

```{r obs-sim-scatter}
obs_sim <- make_obs_sim_dt()
plot_obs_sim_scatter(obs_sim, colour_by = "period")
```

```{r residuals}
res <- make_residual_dt()
plot_residuals(res)
```

```{r metrics}
perf <- make_performance_dt()
plot_performance_metrics(perf, thresholds = c(NSE = 0.6, KGE = 0.6))
```

---

## Condition assessment

```{r condition-radar}
cond <- make_condition_dt()
plot_condition_factors(cond)
```

```{r condition-register}
reg <- make_register_dt()
plot_condition_register(reg)
```

---

## Model cascade

The cascade diagram requires `ggraph` and `igraph`:

```{r cascade, eval = requireNamespace("ggraph", quietly = TRUE) && requireNamespace("igraph", quietly = TRUE)}
conn <- make_connections_dt()
reg  <- make_register_dt()
plot_model_cascade(conn, reg)
```
